% !TEX encoding = UTF-8 Unicode
% !TEX root = ..\main.tex
% !TEX spellcheck = en-US
%%=========================================
\addcontentsline{toc}{section}{Abstract}

%==========
% Abstract
%==========
%1. State the problem.
%2. Say why it's an interesting problem.
%3. Say what your solution achieves.
%4. Say what follows from your solution.

% Context, objective, method, results, conclusion
\section*{Abstract}
\textbf{Context}: Today, software is contributing a substantial part of new functionalities and innovations of the embedded industry. With size and complexity of the embedded software growing as time the time goes, additional challenges arises, including implicit assumptions of technical debt. Technical debt refers to situations where shortcuts are taken in technical decisions. Technical debt has been identified as one of the key reasons to software system projects failures. Accumulation of technical debt may reduce the dependability and maintainability of the embedded systems.

\textbf{Objective}: The goal of this study is to compare existing research on technical debt and embedded systems, with the insights and experiences of traditional software and embedded system practitioners from the industry. We will explore and understand the causes of technical debt, as well as approaches for managing technical debt in embedded systems.  

\textbf{Research Method}: This research starts by conducting a literature review to get an overview within the field of technical debt and embedded systems. Furthermore, four people from different companies were interviewed using semi-structured interviews. Two of them works with traditional software development, while the last two works with embedded system development. 

\textbf{Results}: The results consists of the knowledge similar to the reseach within technical debt, and embedded software quality. There are many similarities between the causes and management practices of technical debt. The results shows that technical debt is mostly formed as a result of intentional decisions to reach deadlines. However, the results revealed that the embedded system industry has more control over technical debt than traditional software industry. The results also revealed that neither of the participants had any specific management plan for reducing technical debt, but several practices were identified. The results may help companies to understand the existing practices of technical debt management, and use it to improve their own processes.